Modi normali di oscillazione del Sole (Presentazione)

### 2017-06-17 MSS.tex
mf

\begin{scope}[scale=0.5,transform shape,every node/.style={scale=0.6}]
\matrix[matrix of nodes,column sep={60pt,between origins},row
    sep={15pt,between origins}] (s)
  {
Reazione &  $S(0) (keVb)$ & \parbox{2cm}{\centering Incertezza su $S(E_G) (\%)$}\\
$p(p,\APelectron\Pnue)d$ & $(4.01 \pm 0.04)10^{-22}$ & $\pm 0.7$\\
$d(p,\Pphoton)\cel{He}{3}{}{}$ & ${2.14}10^{-4}\substack{+0.17 \\ -0.16}$ & $\pm 7.1$\\
$\cel{He}{3}{}{}(\cel{He}{3}{}{},2p)\cel{He}{4}{}{}$ & $(5.21 \pm 0.27)10^{-3}$ & $\pm 4.3$\\
$\cel{He}{3}{}{}(\cel{He}{4}{}{},\Pphoton)\cel{Be}{7}{}{}$ & $0.56 \pm 0.03$ & $\pm 5.1$\\
$\cel{He}{3}{}{}(p,\APelectron\Pnue)\cel{He}{4}{}{}$ & $(8.6 \pm 2.6)10^{-20}$ & $\pm 30$\\
$\cel{Be}{7}{}{}(\Pelectron,\Pnue)\cel{Li}{7}{}{}{\ }^{I}$ & $ $  & $\pm 2.0$\\
$p(p\Pelectron,\Pnue)d{\ }^{II}$& $ $ & $\pm 1.0$\\
$\cel{Be}{7}{}{}(p,\Pphoton)\cel{B}{8}{}{}$& $(2.08 \pm 0.16)10^{-2}$ & $\pm 7.5$\\
%14N(p,7)150 XI.A 1.66 \pm 0.12 (-3.3 \pm 0.2) x 10-3 b (4.4 \pm 0.3) x 10-5 a \pm 7.2
  };
\draw[]({$(s-1-1)!.5!(s-1-2)$} |- s.north) -- ({$(s-1-1)!.5!(s-1-2)$} |- s.south);
\draw[]({$(s-1-2)!.5!(s-1-3)$} |- s.north) -- ({$(s-1-2)!.5!(s-1-3)$} |- s.south);
\node[fit=(s-1-1.south) (s-1-2.south) (s-1-3.south),inner sep=0pt] (R2) {};
\draw[] (R2.south -| s.west) -- (R2.south -| s.east);
 \end{scope}

>>>>

\begin{scope}[scale=0.5,transform shape,every node/.style={scale=0.6}]
\matrix[matrix of nodes,column sep={60pt,between origins},row
    sep={15pt,between origins}] (s)
  {
Reazione \&  $S(0) (keVb)$ \& \parbox{2cm}{\centering Incertezza su $S(E_G) (\%)$}\\
$p(p,\APelectron\Pnue)d$ \& $(4.01 \pm 0.04)10^{-22}$ \& $\pm 0.7$\\
$d(p,\Pphoton)\cel{He}{3}{}{}$ \& ${2.14}10^{-4}\substack{+0.17 \\ -0.16}$ \& $\pm 7.1$\\
$\cel{He}{3}{}{}(\cel{He}{3}{}{},2p)\cel{He}{4}{}{}$ \& $(5.21 \pm 0.27)10^{-3}$ \& $\pm 4.3$\\
$\cel{He}{3}{}{}(\cel{He}{4}{}{},\Pphoton)\cel{Be}{7}{}{}$ \& $0.56 \pm 0.03$ \& $\pm 5.1$\\
$\cel{He}{3}{}{}(p,\APelectron\Pnue)\cel{He}{4}{}{}$ \& $(8.6 \pm 2.6)10^{-20}$ \& $\pm 30$\\
$\cel{Be}{7}{}{}(\Pelectron,\Pnue)\cel{Li}{7}{}{}{\ }^{I}$ \& $ $  & $\pm 2.0$\\
$p(p\Pelectron,\Pnue)d{\ }^{II}$\& $ $ \& $\pm 1.0$\\
$\cel{Be}{7}{}{}(p,\Pphoton)\cel{B}{8}{}{}$\& $(2.08 \pm 0.16)10^{-2}$ \& $\pm 7.5$\\
%14N(p,7)150 XI.A 1.66 \pm 0.12 (-3.3 \pm 0.2) x 10-3 b (4.4 \pm 0.3) x 10-5 a \pm 7.2
  };
\draw[]({$(s-1-1)!.5!(s-1-2)$} |- s.north) -- ({$(s-1-1)!.5!(s-1-2)$} |- s.south);
\draw[]({$(s-1-2)!.5!(s-1-3)$} |- s.north) -- ({$(s-1-2)!.5!(s-1-3)$} |- s.south);
\node[fit=(s-1-1.south) (s-1-2.south) (s-1-3.south),inner sep=0pt] (R2) {};
\draw[] (R2.south -| s.west) -- (R2.south -| s.east);
 \end{scope}
